---
title: "data memo"
author: "James(Changhwan) Han (3923257)"
date: "4/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries
```{r}
library(readr)
library(magrittr)
```


```{r}
happiness <- read_csv("C:\\Users\\james\\OneDrive\\Desktop\\PSTAT 231\\final project\\final-project-data-memo\\world-happiness-report-2021.csv")

happiness %>%
  head()
```
```{r}
names(happiness)
```

# An overview of my dataset
-What does it include? \
-Where and how will you be obtaining it? Include the link and source. \
-About how many observations? How many predictors? \
-What types of variables will you be working with? \
-Is there any missing data? About how much? Do you have an idea for how to handle it? \
\
The dataset includes happiness scores and rankings.\
I obtained this dataset from Kaggle, https://www.kaggle.com/datasets/ajaypalsinghlo/world-happiness-report-2021 \
There are 149 observations and we are going to use 6 predictors in the dataset; Logged GDP per capita, Social support, Healthy life expectancy, Freedom to make life choices, Generosity, and Perceptions of corruption. \
There are no missing values so we don't have to worry about how to handle it.

# An overview of your research question
What variable(s) are you interested in predicting? What question(s) are you interested in answering? \
Name your response/outcome variable(s) and briefly describe it/them. \
Will these questions be best answered with a classification or regression approach? \
Which predictors do you think will be especially useful? \
Is the goal of your model descriptive, predictive, inferential, or a combination? Explain. \
\
I'm interested in predicting happiness score using different predictors.
The response would be Ladder score in the dataset scored in a scale of 0 to 10. \
This question would be best answered with a regression approach because the response variables are quantitative. \
I'm expecting healthy lift expectancy and freedom to make life choices to be really useful in predicting happiness score. \
My goal of the model is predictive because my aim is to predict happiness score. \



# Your proposed project timeline
When do you plan on having your data set loaded, beginning your exploratory data analysis, etc? \
Provide a general timeline for the rest of the quarter. \
\
I already have the data set loaded and I am planning to spend 3-4 hours at least on the weekends for the rest of the quarter. \
For the first half of the timeline, I would focus on data processing and identifying relationships between variables. For the rest half of the timeline, I would focus on choosing a right model and data visualizing. \

# Any questions or concerns
Are there any problems or difficult aspects of the project you anticipate? \
Any specific questions you have for me/the instructional team?\
\
I am thinking about how to deal with the columns associated with dystopia, a hypothetical country that has values equal to the world's lowest national averages for each of the six factors. \
